\bf\mftitle

### 2011-02-16 doc/jInfer/autoeditor/autoeditor.tex
Documentation: AutoEditor.

TODO dopisat, translate, odkaz niekam na popis modulov

\code{Layout}s su implementovane pomocou modularneho systemu. Pre vyrobu noveho je treba vyrobit triedu implementujucu LayoutFactory a spravne ju oanotovat.

@@

@@

Constructor has one argument, instance of \code{Layout} class created from an automaton, typically by \code{LayoutHelperFactory} (see \ref{subsubsection:LayoutHelperFactory}).

@@

Tried \code{PluggableVisualizer} je rozsirenim triedy \code{Visualizer}, ktora poskytuje navyse jednoduchy sposob ako zapajat mouse pluginy.

Mouse plugin je trieda JUNGu, ktore rozsiruje moznosti Visualizera o pracu s mysou (vyberanie stavov, zoom, ...). Spomenut uz existujuce pluginy a ref.

@@

Metody:

addGraphMousePlugin()
setVertexLabelTransformer()
replaceVertexLabelTransformer()
setEdgeLabelTransformer()
replaceEdgeLabelTransformer()

>>>>

\code{Layout}s can be implemented using the modular system. To create a new implementation of \code{Layout} interface, it is needed to create a new class implementing \code{LayoutFactory} interface (package \code{package cz.cuni.mff.ksi.jinfer.autoeditor.automatonvisualizer.layouts}) and annotate it by the following code.

\begin{verbatim}
@ServiceProvider(service = LayoutFactory.class)
\end{verbatim}

Created implementation will be shown in project properties in the \code{Layout} selection.\\

System of modules is described in detail in TODO ref.

@@

This section describes classes implementing basic common functionality that are supposed to be extended to create a new suitable visualization of automata for a particular method of inference. The new visualization may involve a brand new GUI panel with buttons with various functions, user interaction like selecting states or edges and others.\\

@@

Constructor has one argument, instance of \code{Layout} interface created from an automaton, typically by \code{LayoutHelperFactory} (see \ref{subsubsection:LayoutHelperFactory}).

@@

\code{PluggableVisualizer} class is extension of \code{Visualizer} class, which primarily provides an easy way to plug \emph{graph mouse plugins}.\\

\emph{Graph mouse plugin}s are classes implementing JUNG \code{GraphMousePlugin} interface and their purpose is to enhance \code{Visualizer} with mouse support.\\

By default, instance of \code{PluggableVisualizer} is constructed with two plugins enabled. They are \code{ScalingGraphMousePlugin}, providing zooming, and \code{TranslatingGraphMousePlugin}, providing translating the displayed automaton in the x and y direction. In the most cases, these plugins are useful but if they are not wanted they can be removed using methods \code{getGraphMousePlugins()} and \code{removeGraphMousePlugin()}.\\

@@

Public (not inherited) methods of \code{PluggableVisualizer}.

TODO
\begin{itemize}
	\item addGraphMousePlugin()
	\item removeGraphMousePlugin()
	\item getGraphMousePlugins()
	\item setVertexLabelTransformer()
	\item replaceVertexLabelTransformer()
	\item setEdgeLabelTransformer()
	\item replaceEdgeLabelTransformer()
\end{itemize}
